---
title: "Movie_Ratings_Project"
author: "Kashish Gupta"
date: "2024-11-01"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Analyzing Movie Ratings**

#INTRODUCTION

-   Title: Movies' ratings versus user votes
-   Usually, we can find a lot of information online about the ranking of movies, universities, supermarkets, etc. We can use these data to supplement information from another database or facilitate trend analysis. However, it's not easy to choose the right criterion because several might be interesting (e.g., movies' ratings and user votes). In this project, we want to extract information on the most popular movies from early 2020 and check if the ratings are in alignment with the votes. If yes, then we can consider either one or the other without loss of information.

##ABOUT THE GOAL:
-  we want to extract data from the top 30 movies between March and July 2020. We can extract various details, including a movie's title, description, actors, director, genre, runtime, and ratings.
-  Then, we want to check whether ratings correlate to user votes.

# Loading the packages
```{r load packages}
install.packages("rvest")
install.packages("dplyr")
install.packages("ggplot2")
install.packages("readr")
install.packages("stringr")
install.packages("tibble")

library("rvest")
library("dplyr")
library("ggplot2")
library("readr")
library("stringr")
library("tibble")

```

#loading the web page
```{r load}
url <- "https://dataquestio.github.io/web-scraping-pages/IMDb-DQgp.html"
wp_content = read_html(url)
```

# String Manipulation Reminder
```{r}
as.numeric("10.50")
as.numeric(c("14.59", "3.14", "55"))
readr::parse_number(c("14 min", "17,35", "(2012)", "1,2,3,4"))
stringr::str_trim(" Spaces before and after should disappear    ")
```
# Extracting Elements from the Header
First, we want to extract the movies' titles and release years.
```{r}
# Extracting the movie's titles
## Finding the title CSS selector
title_selector <- ".lister-item-header a"
## Identifying the number of elements this selector will select from Selector Gadget 
n_title <- 30
## Extracting the movie titles combining the `html_nodes()` and `html_text()` function
titles <- wp_content %>% 
  html_nodes(title_selector) %>% 
  html_text()
## Printing titles vector
titles
# Extracting the movie's years
## Using a process similar to the one we used to extract the titles
year_selector <- ".lister-item-year"
n_year <- 30
years <- wp_content %>% 
  html_nodes(year_selector) %>% 
  html_text()
## Converting the years from character to numeric data type
years <- readr::parse_number(years)
## Printing years vector
years
```

# Extracting Movie's Features
We want now to extract the movie's runtimes and genres.
```{r}
# Extracting the movie's runtimes
## Finding the runtime CSS selector
runtime_selector <- ".runtime"
## Identifying the number of elements this selector will select from Selector Gadget 
n_runtime <- 30
## Extracting the movie runtimes combining the `html_nodes()` and `html_text()` function
runtimes <- wp_content %>% 
  html_nodes(runtime_selector) %>% 
  html_text()
## Converting the runtimes from character to numeric data type
runtimes <- readr::parse_number(runtimes)
## Printing runtimes vector
runtimes
# Extracting the movie's genres
## Extracting the movie genres using a similar process as previously
genre_selector <- ".genre"
n_genre <- 30
genres <- wp_content %>% 
  html_nodes(genre_selector) %>% 
  html_text()
## Removing whitespaces at the end of genre characters
genres <- stringr::str_trim(genres)
## Printing genres vector
genres
```

# Extract the movies' user ratings.
We're now extracting the user ratings and metascores.
```{r}
# Extracting the movies user rating
## Find the use rating CSS selector and assign the result to a variable.
user_rating_selector <- ".ratings-imdb-rating"
## Identify the number of elements this selector will select from Selector Gadget
n_user_rating <- 29
## Extract the user ratings, combining the html_nodes() and html_attr() functions
user_ratings <- wp_content%>%
  html_nodes(user_rating_selector)%>%
  html_attr("data-value")
## Convert the user ratings from character to numeric data type
user_ratings <- as.numeric(user_ratings)
## Print the user_ratings vector
user_ratings

#Extract the movies' metascores
## Find the metascore CSS selector and assign the result to a variable.
metascore_selector <- ".metascore"
## Identify the number of elements this selector will select from Selector Gadget
n_metascore <- 25
## Extract the metascores, combining the html_nodes() and html_attr() functions
metascores <- wp_content%>%
  html_nodes(metascore_selector)%>%
  html_text()
## Remove whitespaces at the end of metascores and convert them into numeric data type
metascores <- stringr::str_trim(metascores)
metascores <- as.numeric(metascores)
## Print the metascores vector
metascores
```
# Extracting the Movies' Votes
```{r}
# Extract the movies' votes
## Find the vote CSS selector, and assign the result to a variable
vote_selector <- ".sort-num_votes-visible :nth-child(2)"
## Identify the number of elements this selector will select from Selector Gadget
n_vote <- 29
## Extract the votes, combining the html_nodes() and html_text() functions
votes <- wp_content%>%
  html_nodes(vote_selector)%>%
  html_text()
## Convert the votes from character to numeric data type
votes <- readr::parse_number(votes)
## Print the votes vector
votes

```
# Dealing with Missing Values
We've extracted the titles, years, runtimes, genres, user ratings, metascores, and votes from our web page.

- We can now combine them using the tibble() function. Since we're missing some data, this operation will throw an error.

- Exploring the web page again, we notice that the 17th movie is partly the cause of this problem. Furthermore, movies 2, 3, 4, 17, and 29 don't have metascores.

- Introduce NA values in the metascores vector. - Remove the 17th element from all the vectors with a length of 30.

To insert NA into the metascores vector at positions 2, 3, 4, 17, and 29, we have to provide the following positions to our function: 1, 1, 1, 13, and 24. They are the positions after which to insert NA.
```{r}
# Copy-pasting the `append_vector()` in our Markdown file
append_vector <- function(vector, inserted_indices, values){

  ## Creating the current indices of the vector
  vector_current_indices <- 1:length(vector)

  ## Adding small amount of values (between 0 and 0.9) to the `inserted_indices`
  new_inserted_indices <- inserted_indices + seq(0, 0.9, length.out = length(inserted_indices))

  ## Appending the `new_inserted_indices` to the current vector indices
  indices <- c(vector_current_indices, new_inserted_indices)

  ## Ordering the indices
  ordered_indices <- order(indices)

  ## Appending the new value to the existing vector
  new_vector <- c(vector, values)

  ## Ordering the new vector wrt the ordered indices
  new_vector[ordered_indices]
}
# Using the append_vector() function to insert NA into the metascores vector after the positions 1, 1, 1, 13, and 24.
metascores <- append_vector(metascores,c(1, 1, 1, 13, 24), NA)
metascores
# Remove the 17th element from the vectors: titles, years, runtimes, genres, and metascores
## Save the result back to these vectors
titles <- titles[-17]
years <- years[-17]
runtimes <- runtimes[-17]
genres <- genres[-17]
metascores <- metascores[-17]
```
# Putting It All Together and Visualizing
- Now that we've dealt with missing values, we can create a boxplot to show the number of votes against the user ratings.
- We determine that the lowest- and highest-rated films have the lowest and highest votes. There is also a linear correlation between the ratings and votes, on average.
```{r}
# Create a dataframe with the data we previously extracted: titles, years, runtimes, genres, user ratings, metascores, and votes
## Keep only the integer part of the user ratings using the floor() function. For example, 3.4 becomes 3.
movie_df <- tibble::tibble("title" = titles,
                           "year" = years,
                           "runtime" = runtimes,
                           "genre" = genres,
                           "rating" = floor(user_ratings),
                           "metascore" = metascores,
                           "vote" = votes)
#Create a boxplot that shows the number of votes against the user rating
ggplot(data = movie_df,
       aes(x = rating, y = vote, group = rating)) +
  geom_boxplot()
```



